### 2017-05-13 paper/evaluation.tex
minor change to rq6
pass on eval

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a machine with more cores compared to the one described in
Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
processor machine with 80 virtual CPUs (40 cores with two native
threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
Tarr (64-bit version). This experiment uses configuration \ForkSeq{}
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
as the goal is to evaluate the impact on runtime of spawning a growing number of
JVMs in different CPUs.  Furthremore, we selected subject
\subjectScalability{} as it represents the case of a long-running test
suite (see Figure~\ref{tab:speedup}) with test cases distributed
across many test classes (194 test classes for \subjectScalability{}).
Note that a test class is the smallest unit that can be used to spawn
a test job on a JVM and that we have no control over which test
classes will be assigned to which JVM that the build system forks.

Figure~\ref{fig:scalability} shows the reduction of running times as
more CPUs contribute to the execution.  \Fix{elaborate...}

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupTwo{}:}~\emph{...}
  \end{minipage}
}
\end{center}

>>>>

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a machine with more cores compared to the one described in
Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
processor machine with 80 virtual CPUs (40 cores with two native
threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
Tarr (64-bit version). This experiment uses configuration \emph{\ForkSeq{}}
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.2\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
as the goal is to evaluate the impact on runtime of spawning a growing number of
JVMs in different CPUs.  We selected subject
\subjectScalability{} in this experiment as it represents the case of a long-running test
suite (see Figure~\ref{tab:speedup}) with test cases distributed
across many test classes (194 test classes for \subjectScalability{}).
Note that a test class is the smallest unit that can be used to spawn
a test job on a JVM and that we have no control over which test
classes will be assigned to which JVM that the build system forks.

Figure~\ref{fig:scalability} shows the reduction in running times as
more CPUs contribute to the execution.  We ran this experiment for a
growing number of cores 1, 3, ..., 39.  The plot shows results up to
17 cores as it is clear the tendency.  We noticed that improvements
are marginal after three cores, which is the basic setup we used in
other experiments.  This saturation is justified by the presence of a
single test class, \CodeIn{org.mapdb.WALTruncat}, containing 15 test
cases that take over four minutes to run.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupTwo{}:}~\emph{Results suggest that
      execution FC0 scales with additional cores but there is a bound
      on the speedup one can get related to how well the test suite is
      balanced across test classes.}
  \end{minipage}
}
\end{center}
